### 2023-03-27 uvp6_part.qmd
Abstract

Millions of images of oceanic particles have been acquired with ship-based imaging instruments. The task of labeling images is time consuming but necessary to train classification models using artificial intelligence algorithms. Autonomous Underwater Vehicles (AUVs) such as Biogeochemical-Argo floats (BGC-Argo) have revolutionized our understanding of oceanic systems but they are flawed by their battery life and by the time they can spend at the ocean surface to transmit their data. In this paper, we show how we developed the first zooplankton classification model for AUVs using the Underwater Vision Profiler 6 (UVP6). To this end, we used a features-based classifier called eXtreme Gradient Boosting (XGBoost) adapted to specific energy constraints imposed by profiling floats and we compared its performance with a state-of-the-art convolutional neural network as if energy was not a limiting factor. In addition, we show how we dealt with a highly imbalanced data set towards marine snow (\> 80% of detritus) and what were the compromises to improve the classification scores of biological classes. Finally, we show the classification report (precision and recall for each label) of the final classification model and use it to analyse some preliminary results from BGC-Argo floats deployed in the Labrador Sea.

>>>>

Millions of images of oceanic particles have been acquired with ship-based imaging instruments. The identification of objects on images is time consuming for human operators but can be accelerated using artificial intelligence algorithms. Autonomous Underwater Vehicles (AUVs) such as Biogeochemical-Argo floats (BGC-Argo) have revolutionized our understanding of oceanic systems but have limited battery life and must spend as little time as possible at the ocean surface to transmit their data, which means that images cannot be transmitted. In this paper, we describe an image classification model embedded in the Underwater Vision Profiler 6 (UVP6) that is appropriate to be run on the limited power and bandwidth of AUVs. To this end, we computed simple global features of images of objects of interest and gradient boosted trees as a classifier. We compared its performance with a state-of-the-art convolutional neural network, which is much more energy demanding. In addition, we show how we dealt with class imbalance (\> 80% of images are marine snow) and what were the compromises to improve the classification scores of biological classes. Finally, we show the classification report (precision and recall for each label) of the final classification model and use it to analyze preliminary results from BGC-Argo floats deployed in the Labrador Sea.
